# Results and Discussion

## FISHING

```{r HistoricText, echo=FALSE}

# not able to query in detail the fishing days and block rejections/replacements, taken from notes

```
The `r yr` survey was `r days` days long and divided into two legs of `r legone` and `r legtwo` days. A total of 27 fishing days were recorded due to mechanical issues (one day) on the first leg and inclement weather (13 days) on the second leg.   

Of the 91 original blocks for the StRS portion of the survey, ten were replaced at-sea and four blocks were rejected with no valid substitutes, for a total of 87 blocks fished (Table \@ref(tab:table1)). Of the ten replacements, one was revoked after on-ground inspection, three were located within unfishable habitat, four had failed to meet depth strata requirements, one was located in a GHNMCA protected area and one generated an error.

```{r CatchRateText, echo=FALSE}
  # -- generate the lowest uncertainity and corresponding year for catch rate paragraph

  dtStRS   <-   " select  * from dbo.GENERIC_GFBIO_TRAPS order by year"  # -- must update view GENERIC_GFBIO_TRAPS
  #datStRS  <-   GetSQLData(dtStRS,"Sablefish")                          # read from SQL Server
  #write.table(datStRS, file = paste(path,"results01.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
  datStRS  <-  read.csv(paste(path,'results01.csv',sep=''), header=T)  # read from csv
  odbcCloseAll()

  datRD    <-   datStRS[ datStRS$SABLE.SET.TYPE=="StRS", ] # --  pick out the random sets
  dat      <-   datRD[ ! is.na(datRD$SABLE.SET.TYPE), ]
  yrs      <-   unique(datRD$year)   # -- get unique years
  nyrs     <-   length(yrs)
  
  data.cv  <- data.frame( year   <- numeric(),
                          value1 <- numeric(),
                          value2 <- numeric(),
                          value3 <- numeric() )
  
  data.mn <- data.frame(  year   <- numeric(),
                          value1 <- numeric(),
                          value2 <- numeric(),
                          value3 <- numeric() )

  # -- iterate through the years building depth boxplots to get cv's and mean counts
  for (i in 1:nyrs)
     {    yrdat          <- datRD[datRD$year==yrs[i],]      # -- get the year dataset
          bxdat          <- split(yrdat$CPUE.SABLE.COUNT / yrdat$CPUE.TRAPS, as.character(yrdat$SABLE.DEPTH.GROUP))  # split by depth
          dpth.mean      <- sapply(bxdat, mean, na.rm=T)    # -- add the mean by depth  points
          std.dev        <- sapply(bxdat, sd, na.rm=T)
          names(data.cv) <- c("year", "RD1", "RD2", "RD3")  # -- store cv's
          names(data.mn) <- c("year", "RD1", "RD2", "RD3")  # -- store mean counts by depth
          data.cv        <- rbind(data.cv,c(yrs[i],round(std.dev/dpth.mean,2)))
          data.mn        <- rbind(data.mn,c(yrs[i],round(dpth.mean,0)))
      }
  
          RD1.cvlow      <- min(data.cv$RD1)
          RD1.cvlowyr    <- data.cv$year[data.cv$RD1==RD1.cvlow]
          RD2.cvlow      <- min(data.cv$RD2)
          RD2.cvlowyr    <- data.cv$year[data.cv$RD2==RD2.cvlow]
          RD3.cvlow      <- min(data.cv$RD3)
          RD3.cvlowyr    <- data.cv$year[data.cv$RD3==RD3.cvlow]
          
    # -- type data.mn in the Console to view the shallow, middle and deep depth stratums CPUE for 
    # -- descriptive paragraph below
  
```
## CATCH PER UNIT EFFORT (CPUE) 

The sablefish survey of `r yr` have documented recent changes in the sablefish population structure.

### Stratified Random Set CPUE

Across all years, the highest annual CPUE (kg/trap) typically occured in the middle depths (450-850 m). In recent years, an increase in CPUE started in 2015 and a consistent rise in CPUE began in 2017 (Figure \@ref(fig:figure4)).  This increase was observed in nearly all depth strata (RD~1~ to RD~2~) and area strata (SD~1~ to SD~5~) (Figure \@ref(fig:figure5)).  The observed catch by weight pattern was accompanied by an increase in the number of fish per trap.  However, the large estimated numbers of fish were highly variable (+-95% CI) (Figure \@ref(fig:figure6)).  The observed mean weights indicated a three year declining trend beginning in 2017 in half of the area-depth strata. Little or no trend was seen in the remaining strata (Figure \@ref(fig:figure7)).

```{r SpeciesCompositionText, echo=FALSE}
  # -- taxonomic top 5 group count StRS
   topStRS      <- paste("select top (5) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, ",
                         "sum(CATCH_WEIGHT) AS catchkg ",
                         "from dbo.GFBIO_RESEARCH_CATCH ",
                         "group by SABLE_SET_TYPE, Year, SPECIES_CODE, ",
                         "SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME ",
                         "having (SABLE_SET_TYPE = N'StRS') and ",
                         "(SPECIES_CODE <> N'455') and (Year = ",yr,") ",
                         "order by catchkg DESC", sep="") 
   #topStRSsp    <- GetSQLData(topStRS,"Sablefish") 
   #write.table(topStRSsp, file = paste(path,"results02.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   topStRSsp  <-  read.csv(paste(path, 'results02.csv',sep=''), header=T) 
   
   topStRSsp1   <- tolower(as.character(topStRSsp[1,1]))                     # -- StRS top 5 species names
   topStRSsc1   <- firstup(tolower(as.character(topStRSsp[1,2])))    # -- StRS top 5 species science names
   
   topStRSsp2   <- as.character(topStRSsp[2,1])                       
   topStRSsc2   <- firstup(tolower(as.character(topStRSsp[2,2])))   
   
   topStRSsp3   <- tolower(as.character(topStRSsp[3,1]))                      
   topStRSsc3   <- firstup(tolower(as.character(topStRSsp[3,2])))
   
   topStRSsp4   <- tolower(as.character(topStRSsp[4,1]) )                    
   topStRSsc4   <- firstup(tolower(as.character(topStRSsp[4,2])))  
   
   topStRSsp5   <- tolower(as.character(topStRSsp[5,1]))                      
   topStRSsc5   <- firstup(tolower(as.character(topStRSsp[5,2]))) 

 
 # -- species composition counts for StRS sets 
   spc          <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish as int))) as tRound,  ",
                                "dbo.fnIntegerToWords(SUM(Rockfish))     as tRock,   ",
                                "dbo.fnIntegerToWords(SUM(Flatfish))     as tFlat,   ",
                                "dbo.fnIntegerToWords(SUM(Invertebrate)) as tInvert, ",
                                "dbo.fnIntegerToWords(SUM(Mammal))       as tMammal, ",
                                "dbo.fnIntegerToWords(SUM(Bird))         as tBird,   ",
                                "dbo.fnIntegerToWords(SUM(counter))      as total    ",
                                "from (select case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end AS Roundfish, ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, ",
                                "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE from dbo.GFBIO_RESEARCH_CATCH ",
                                "group by ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID,  ",
                                "case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end, SPECIES_CODE  ",
                                "having (SABLE_SET_TYPE = N'StRS') and (Year = ",yr,")) AS RC", sep="")
   #strsSpCom    <- GetSQLData(spc,"Sablefish")
   #write.table(strsSpCom, file = paste(path,"results03.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   strsSpCom   <-  read.csv(paste(path,'results03.csv',sep=''),header=T) 
   
   roundfishS   <- strsSpCom[1,1]
   rockfishS    <- strsSpCom[1,2]
   flatfishS    <- strsSpCom[1,3]
   invertS      <- strsSpCom[1,4]
   mammalS      <- strsSpCom[1,5]
   birdS        <- strsSpCom[1,6]
   #totalS       <- firstup(as.character(strsSpCom[1,7])) # taxonomic unit count for StRS with capital
   totalS       <- as.character(strsSpCom[1,7]) # taxonomic unit count for StRS


```

## CATCH COMPOSITION

A total of `r totalS[1]` taxonomic groups were represented in the catches in StRS sets in `r yr` (Table \@ref(tab:table3)).  These included `r roundfishS[1]` roundfish species, `r rockfishS[1]` rockfish species, `r flatfishS[1]`  flatfish species and `r invertS[1]` invertebrate species. Other than sablefish, the most common species, by weight,  were  `r topStRSsp1[1]` (*`r topStRSsc1`*), `r topStRSsp2` (*`r topStRSsc2`*), `r topStRSsp3` (*`r topStRSsc3`*),   `r topStRSsp4` (*`r topStRSsc4`*) and  `r topStRSsp5` (*`r topStRSsc5`*).   

```{r SamplingWords, echo=FALSE}
    # inline text query Sablefish.dbo.GFBIO_RESEARCH_SAMPLE_DETAILS for the counts of Sablefish from StRS sets
    catchStRS   <- paste("select rt.SABLE_SET_TYPE, ",
                         "SUM(sd.[Total Count])                           AS count, ",
                         "SUM(sd.[Recovered Number])                      AS tagagainlive, ",
                         "SUM(sd.[Recovered Dead Number])                 AS tagdead, ",
                         "SUM(sd.[Tagged Number] + sd.[Recovered Number]) AS tagrelease, " ,
                         "SUM(sd.[Fork Len Tag Sample Count])             AS taglengthsample,  " ,
                         "SUM(sd.Sample_count)                            AS samplecount " ,
                         "from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS AS sd INNER JOIN " ,         
                         "dbo.GFBIO_SABLEBIO_TRIP_SET2 AS rt ON " ,
                         "sd.TRIP_ID = rt.TRIP_ID AND  sd.[SET] = rt.SET_NUMBER " ,
                         "where (sd.Year =", yr,") group by rt.SABLE_SET_TYPE",sep="")

    #countStRS   <- GetSQLData(catchStRS,"Sablefish")
    #write.table(countStRS, file = paste(path,"results04.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    countStRS   <-  read.csv(paste(path,'results04.csv',sep=''),header=T) 
    
    # -- Sablefish.dbo.procReport_Survey_LenMF pulls length data from table GFBIO_SABLEBIO_VW 
    # -- from procedure Build_BIO_Sablefish_Tables for the histogram of lengths
    
    lendat     <-   "exec procReport_Survey_LenMF"
    #lendata    <-   GetSQLData(lendat,"Sablefish")
    #write.table(lendata, file = paste(path,"results05.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    lendata   <-    read.csv(paste(path,'results05.csv',sep=''),header=T) 
    
    # late addition for the average lengths per year in text
    lenstats  <- "exec procRReport_Survey_LenAvg"
    dat       <- GetSQLData(lenstats,"Sablefish")
    write.table(dat, file = paste(path,'results05b.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    dat       <- read.csv(paste(path,'results05b.csv',sep=''), header=T)
    mavgyr1   <- dat[dat$sex==1 & dat$YEAR==yr,]   # round(mavgyr1$AvL,1)
    favgyr1   <- dat[dat$sex==2 & dat$YEAR==yr,]   # round(favgyr1$AvL,1)
  
    fdat      <- dat[dat$sex==2,]
    mdat      <- dat[dat$sex==1,]
    
    firstyrfem <-   lendata[lendata$year == yr & lendata$sex == 2,] 
    firstyrmal <-   lendata[lendata$year == yr & lendata$sex == 1,] 
      
    lenMF      <-   lendata[lendata$year <= yr,] 
    brk        <-   seq(min(lenMF$length)-1,max(lenMF$length)+1)
    osex      <-   length(lenMF$length[lenMF$sex==3])
    	
    # -- set up the female data
    females  <-   lenMF$length[lenMF$sex==2]
    females  <-   females[!is.na(females)]
    tf       <-   length(females)                                 # -- count female lengths
    mLf      <-   format(round(mean(females,na.rm=T),1),nsmall=1) # -- mean female length
    stdf     <-   round(sd(females),1)                            # -- standard deviation
    	
    #--  set up the male data
    males    <-   lenMF$length[lenMF$sex==1]
    tm       <-   length(males)                                   # -- count male lengths
    mLm      <-   format(round(mean(males,na.rm=T),1),nsmall=1)   # -- mean male length
    stdm     <-   round(sd(males),1)                              # -- standard deviation
 
    # --  StRS year one by spatial and depth strata:  count/mean of samples for fork length and tagged fish fork lengths
     bio      <-   paste("select locality, depth, PropMales, PropFemales, ",
                         "MalesMnFkLen, FemalesMnFkLen, TaggedMnFkLen ",
                         "from gfbio_sable_bio_summary ",
                         "where depth is not null and year = ",yr,
                         "order by Locality,Depth", sep="")
     biosumm  <-   GetSQLData(bio,"Sablefish")
     write.table(biosumm, file = paste(path,"results06.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
     biosumm   <-    read.csv(paste(path,'results06.csv',sep=''),header=T) 

     colnames(biosumm) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
     biosumm$Spatial   <-  cleanf(biosumm$Spatial)  # use the remove duplicates function

     #  -- sum the count of length values for the table columns
     biosumm[16,3]     <-  round((biosumm[1,3] + biosumm[2,3] + biosumm[3,3])/ 3, 2)  # --  males S1 average proportions
     biosumm[16,4]     <-  round((biosumm[1,4] + biosumm[2,4] + biosumm[3,4])/ 3, 2)  # --  females S1 average proportions
     biosumm[16,5]     <-  round((biosumm[1,5] + biosumm[2,5] + biosumm[3,5])/ 3, 0)  # --  males S1 average fork len
     biosumm[16,6]     <-  round((biosumm[1,6] + biosumm[2,6] + biosumm[3,6])/ 3, 0)  # --  females S1 average fork len 
     biosumm[16,7]     <-  round((biosumm[1,7] + biosumm[2,7] + biosumm[3,7])/ 3, 0)  # --  tagged S1 average fork len
      
     biosumm[17,3]     <-  round((biosumm[4,3] + biosumm[5,3] + biosumm[6,3])/ 3, 2)   # -- S2
     biosumm[17,4]     <-  round((biosumm[4,4] + biosumm[5,4] + biosumm[6,4])/ 3, 2)
     biosumm[17,5]     <-  round((biosumm[4,5] + biosumm[5,5] + biosumm[6,5])/ 3, 0)
     biosumm[17,6]     <-  round((biosumm[4,6] + biosumm[5,6] + biosumm[6,6])/ 3, 0)
     biosumm[17,7]     <-  round((biosumm[4,7] + biosumm[5,7] + biosumm[6,7])/ 3, 0)
      
     biosumm[18,3]     <-  round((biosumm[7,3] + biosumm[8,3] + biosumm[9,3])/ 3, 2)   # -- S3
     biosumm[18,4]     <-  round((biosumm[7,4] + biosumm[8,4] + biosumm[9,4])/ 3, 2)
     biosumm[18,5]     <-  round((biosumm[7,5] + biosumm[8,5] + biosumm[9,5])/ 3, 0)
     biosumm[18,6]     <-  round((biosumm[7,6] + biosumm[8,6] + biosumm[9,6])/ 3, 0)
     biosumm[18,7]     <-  round((biosumm[7,7] + biosumm[8,7] + biosumm[9,7])/ 3, 0)
      
     biosumm[19,3]     <-  round((biosumm[10,3] + biosumm[11,3] + biosumm[12,3])/ 3, 2)  # -- S4
     biosumm[19,4]     <-  round((biosumm[10,4] + biosumm[11,4] + biosumm[12,4])/ 3, 2)
     biosumm[19,5]     <-  round((biosumm[10,5] + biosumm[11,5] + biosumm[12,5])/ 3, 0)
     biosumm[19,6]     <-  round((biosumm[10,6] + biosumm[11,6] + biosumm[12,6])/ 3, 0) 
     biosumm[19,7]     <-  round((biosumm[10,7] + biosumm[11,7] + biosumm[12,7])/ 3, 0) 
      
     biosumm[20,3]     <-  round((biosumm[13,3] + biosumm[14,3] + biosumm[15,3])/ 3, 2)  # --S5
     biosumm[20,4]     <-  round((biosumm[13,4] + biosumm[14,4] + biosumm[15,4])/ 3, 2)
     biosumm[20,5]     <-  round((biosumm[13,5] + biosumm[14,5] + biosumm[15,5])/ 3, 0)
     biosumm[20,6]     <-  round((biosumm[13,6] + biosumm[14,6] + biosumm[15,6])/ 3, 0)  
     biosumm[20,7]     <-  round((biosumm[13,7] + biosumm[14,7] + biosumm[15,7])/ 3, 0)
      
     newdata           <-  rbind(biosumm[1:3,],   biosumm[16,], biosumm[4:6,],  biosumm[17,],
                                 biosumm[7:9,],   biosumm[18,], biosumm[10:12,],biosumm[19,], 
                                 biosumm[13:15,], biosumm[20,])   # r bind the average column results
     newdata$Spatial   <-  cleanf(newdata$Spatial)
     colnames(newdata) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
     
     pdiffS1 <- biosumm[16,3] - biosumm[16,4]  # --  S1 check male - female prop
     pS1     <- sum(pdiffS1 < 0.00)
     if (pS1 == 1)  {wS1="S~1~, "} else {wS1=""} # --  if value negative, more females
      
     pdiffS2 <- biosumm[17,3] - biosumm[17,4]  #  -- S2 check male - female prop
     pS2 <- sum(pdiffS2 < 0.00)
     if (pS2 == 1)  {wS2="S~2~, "} else {wS2=""} 
      
     pdiffS3 <- biosumm[18,3] - biosumm[18,4]   # --  S3 check male - female prop
     pS3 <- sum(pdiffS3 < 0.00)
     if (pS3 == 1)  {wS3="S~3~, "} else {wS3=""}
      
     pdiffS4 <- biosumm[19,3] - biosumm[19,4]  # -- S4 check male - female prop
     pS4 <- sum(pdiffS4 < 0.00)
     if (pS4 == 1)  {wS4="S~4~, "} else {wS4=""}
      
     pdiffS5 <- biosumm[20,3] - biosumm[20,4]  # -- S4 check male - female prop
     pS5 <- sum(pdiffS5 < 0.00)
     if (pS5 == 1)  {wS5="S~5~, "} else {wS5=""}
      
     stratafem    <- paste(wS1,wS2,wS3,wS4,wS5,sep="")         # -- list of S areas where more females
     stratafema   <- substr(stratafem, 1, nchar(stratafem)-2)  # -- trim trailing comma
     stratafemale <- sub(",([^,]*)$", " and\\1", stratafema)   # -- replace last comma with and
    
     #  More females than males were seen in the shallow depth stratum as per yearly trend...
     shallS1 <- sum((biosumm[1,3] - biosumm[1,4])<0.00)
     
     if (shallS1 == 1)  {shallwS1="S~1~, "} else {shallwS1=""}
           shallS2 <- sum((biosumm[4,3] - biosumm[4,4])<0.00)
           
     if (shallS2 == 1)  {shallwS2="S~2~, "} else {shallwS2=""}
           shallS3 <- sum((biosumm[7,3] - biosumm[7,4])<0.00)
            
     if (shallS3 == 1)  {shallwS3="S~3~, "} else {shallwS3=""}      
           shallS4 <- sum((biosumm[10,3] - biosumm[10,4])<0.00)
            
     if (shallS4 == 1)  {shallwS4="S~4~, "} else {shallwS4=""}  
           shallS5 <- sum((biosumm[13,3] - biosumm[13,4])<0.00)
            
     if (shallS5 == 1)  {shallwS5="S~5~, "} else {shallwS5=""}
            
     shallsfem    <- paste(shallwS1,shallwS2,shallwS3,shallwS4,shallwS5,sep="")
     shallsfema   <- substr(shallsfem, 1, nchar(shallsfem)-2)  # -- trim trailing comma
     shallsfemale <- sub(",([^,]*)$", " and\\1", shallsfema)   # replace last comma with and
     
     # -- Assumption that more males than females were seen in the mid depth stratum
     midS1 <- sum((biosumm[2,3] - biosumm[2,4])>0.00)
      
      if (midS1 == 1)  {midwS1="S~1~, "} else {midwS1=""}
          midS2 <- sum((biosumm[5,3] - biosumm[5,4])>0.00)
      
      if (midS2 == 1)  {midwS2="S~2~, "} else {midwS2=""}
            midS3 <- sum((biosumm[8,3] - biosumm[8,4])>0.00)
      
      if (midS3 == 1)  {midwS3="S~3~, "} else {midwS3=""}      
          midS4 <- sum((biosumm[11,3] - biosumm[11,4])>0.00)
      
      if (midS4 == 1)  {midwS4="S~4~, "} else {midwS4=""}  
            midS5 <- sum((biosumm[14,3] - biosumm[14,4])>0.00)
      
      if (midS5 == 1)  {midwS5="S~5~, "} else {midwS5=""}
            
      midsm    <- paste(midwS1,midwS2,midwS3,midwS4,midwS5,sep="")
      midsma   <- substr(midsm, 1, nchar(midsm)-2)      # -- trim trailing comma
      midsmale <- sub(",([^,]*)$", " and\\1", midsma)   # -- replace last comma with and
      
      # -- Assumption that more females than males were seen in the deep depth stratum
      deepS1 <- sum((biosumm[3,3] - biosumm[3,4])<0.00)
      if (deepS1 == 1)  {deepwS1="S~1~, "} else {deepwS1=""}
      deepS2 <- sum((biosumm[6,3] - biosumm[6,4])<0.00)
      if (deepS2 == 1)  {deepwS2="S~2~, "} else {deepwS2=""}
      deepS3 <- sum((biosumm[9,3] - biosumm[9,4])<0.00)
      if (deepS3 == 1)  {deepwS3="S~3~, "} else {deepwS3=""}      
      deepS4 <- sum((biosumm[12,3] - biosumm[12,4])<0.00)
      if (deepS4 == 1)  {deepwS4="S~4~, "} else {deepwS4=""}  
      deepS5 <- sum((biosumm[15,3] - biosumm[15,4])<0.00)
      if (deepS5 == 1)  {deepwS5="S~5~, "} else {deepwS5=""}
      deepsfem    <- paste(deepwS1,deepwS2,deepwS3,deepwS4,deepwS5,sep="")
      deepsfema   <- substr(deepsfem, 1, nchar(deepsfem)-2)   # trim trailing comma
      deepsfemale <- sub(",([^,]*)$", " and\\1", deepsfema)   # replace last comma with and
 
   # -- other fish counts
     othfish      <-   paste(" select species_name, SUM(Sample_count) as count   ",
                             " from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ",
                             " where (Year = ", yr, ") group by species_name, species ",
                             " order by species", sep="")
     otherfish    <-   GetSQLData(othfish,"Sablefish")
     write.table(otherfish, file = paste(path,"results07.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")      
     otherfish    <-   read.csv(paste(path,'results07.csv',sep=''),header=T)
    

```
## SABLEFISH SAMPLING

A detailed breakdown of the fate of the catch in each trap for the `r yr` survey is listed in Appendix \@ref(app:fourth-appendix). 

During the `r yr` StRS, a total of `r format(countStRS[2,2], big.mark=",")` sablefish were caught.   Of that total, `r format(countStRS[2,5], big.mark=",")` were tagged and released and `r format(countStRS[2,7], big.mark=",")` were retained for biological sampling. Of the tagged fish, `r countStRS[2,3]` were previously tagged fish that were re-released with a new tag.  Another `r countStRS[2,4]` previously tagged fish were retained for sampling (Appendix \@ref(app:seventh-appendix)).

Out of the `r format(countStRS[1,2], big.mark=",")` sablefish captured during the `r yr` traditional survey (inlet standardized sets), `r format(countStRS[1,5], big.mark=",")` were tagged and released, `r format(countStRS[1,7], big.mark=",")` were used for biological sampling and `r format(countStRS[1,3], big.mark=",")` were previously tagged fish re-released with a new tag (Appendix \@ref(app:seventh-appendix)). 

Overall, the StRS sets had a higher proportion of females than males over the spatial strata `r stratafemale` with the exception of S~5 where the sex ratio was equal (Table \@ref(tab:table5)).  More females than males were seen in the shallow depth stratum within the spatial strata `r shallsfemale`.  In the mid depth stratum, there were more males than females in `r midsmale`.  The deepest depth stratum saw more females in spatial strata `r deepsfemale`.  

Significant differences in length distributions between female and male sablefish are exhibited in the data collected from the StRS portion of the 2003 - 2020 surveys. The mean fork length ($\bar{x}$) for females was x cm and the mean fork length ($\bar{x}$) for males was x cm (Figure \@ref(fig:figure10)a). 

In `r yr`, the average mean fork length for the `r format(length(firstyrfem$sex), big.mark=",")` females was `r round(favgyr1$AvL,1)` cm  and the average mean fork length for the `r format(length(firstyrmal$sex), big.mark=",")` males was `r round(mavgyr1$AvL,1) ` cm.  The mean length of both females and males reached their lowest mean size since 2003 (Figure \@ref(fig:figure10)b). 

On average, female sablefish grow faster and reach far greater size (Figure \@ref(fig:figure13)a,b) compared to males (Figure \@ref(fig:figure13)c,d).


## SABLEFISH SUB-LEGAL ENCOUNTERS

```{r SablefishAgesText, echo=FALSE}
   # -- provides values for inline text, important to know the last year of ages completed
   # -- sql server procedure:  procRReport_Survey_proportions_at_age which pulls age data from 
   # -- GFBIOSQL.dbo.b21_samples and b22_specimens
   age         <-  paste("select Female_Yr_Total,Age from Report_Survey_GFBIO_Age_MF_Prop where ", 
                         "SetType='StRS' and f=1 and Year=",yr,sep="")
   agedat      <-  GetSQLData(age,"Sablefish")    # --  female age total and count of most aged text captions
   write.table(agedat, file = paste(path,"results08.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   agedat      <-    read.csv(paste(path,'results08.csv',sep=''),header=T)
   
   oldageF     <-  "exec procRReport_Survey_oldAgeFish 2"  # -- oldest female text caption
   oldageFem   <-  GetSQLData(oldageF,"Sablefish")
   write.table(oldageFem, file = paste(path,"results09.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   oldageFem   <-    read.csv(paste(path,'results09.csv',sep=''),header=T)
   
   oldageM     <-  "exec procRReport_Survey_oldAgeFish 1"  # -- oldest male text caption
   oldageMale  <-  GetSQLData(oldageM,"sablefish") 
   write.table(oldageMale, file = paste(path,"results10.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   oldageMale  <-    read.csv(paste(path,'results10.csv',sep=''),header=T) 
   
   oldFem      <-  oldageFem[1,2]                # -- oldest female age
   oldFemYr    <-  oldageFem[1,3]                # -- year captured
   oldMale     <-  oldageMale[1,2]               # -- oldest male age
   oldMaleYr   <-  oldageMale[1,3]               # -- year captured
```

There have been distinct distribution patterns across strata of sub-legal sablefish (<55 cm fork length), following the highly anomalous warm ocean conditions of the “The Blob” [@Bond2015].   More than half of the sub-legal specimens were captured in the southern strata (S~1~) mid-depth waters (RD~2~) in 2014 and shallow waters (RD~1~) in 2015. The sub-legal specimen count was above 50% in both 2017 and 2018 in the northern strata of S~4~ and S~5~  mid-depth waters (RD~2~). In 2019, the sub-legal specimens dominated in all StRS survey strata (S~1~ to S~5~) mid-depth waters (RD~2~). In `r yr`, the.....  (Figure \@ref(fig:figure14)). 

## OTHER FISH SAMPLING

Length, sex, maturity, otoliths and DNA samples were collected for the rougheye/blackspotted rockfish complex.  (Appendix \@ref(app:sixth-appendix)).

## RECOVERED TAGGED SABLEFISH

During the `r yr` sablefish survey, `r countStRS[2,3] + countStRS[1,3]` previously tagged fish were re-released live with a new tag.  DFO has been tagging, releasing and recovering sablefish since 1991.  The highest recovery rate is within the first year of release (Figure \@ref(fig:figure15). Recent release-recovery data (1991-2018) are consistent with Beamish and McFarlane (1988) where about 40-50% of Sablefish are still recovered within 50 km of the release site (Table x).


## SABLEFISH AGES

The highest proportion of male ages in StRS sets for 2003 through to 2011 were 3, 5, 5, 6, 8, 8, 8, 10 and 12 years of age, respectively.  Another cohort appeared in 2012 through to 2016 as 4, 5, 7, 7 and 8 year olds.  A cohort appeared to arrive in 2017 which was dominated by 3 year olds, in 2018 by 5 year olds and in 2019 by x year olds (Figure \@ref(fig:figure16)a).

The highest proportion of female ages in the StRS sets for 2003 through to 2010 were 3, 4, 5, 6, 7, 8, 9 and 10 years of age, respectively. Then, another cohort appeared in 2011 through to 2015, showing up as 3, 4, 5, 6 and 7 year olds.  In 2016, 2017, 2018 and 2019 the highest proportion of female sablefish were ages 3, 4, 5 and x. (Figure \@ref(fig:figure16)b).

Historic data from all samples lists the oldest female sablefish at `r oldFem` years of age collected in `r oldFemYr` where as the oldest male sablefish with the age of `r oldMale` years old was documented for the year `r oldMaleYr`.

```{r SablefishOceanText, echo=FALSE}
     # table SEABIRD_ReportLinePlot created in the Sablefish.dbo.Build_Seabird_tables procedure
     # provide the number values for the inline text
     whatTrap  <-  paste("select * from SEABIRD_ACCEL_byTrap where year =",yr," order by [set]",sep="")
     whatTraps <-  GetSQLData(whatTrap ,"Sablefish")  # in order to be able to comment on which traps the sensors were placed
     write.table(whatTraps, file = paste(path,"results11.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")       
     whatTraps <-  read.csv(paste(path,'results11.csv',sep=''),header=T) 
     
     seabrd    <-  "select * from SEABIRD_ReportLinePlot"
     seabird   <-  GetSQLData(seabrd ,"Sablefish")
     write.table(seabird, file = paste(path,"results12.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")       
     seabird   <-  read.csv(paste(path,'results12.csv',sep=''),header=T) 
     
     yrs         <-  unique(seabird$Year)
     lavtmin     <-  min(seabird$avgtemp[seabird$depth=="Shallow"])
     lavtyr      <- (seabird$Year[seabird$depth=="Shallow" & seabird$avgtemp==lavtmin])
     lavtband1   <- (seabird$latitude[seabird$depth=="Shallow" & seabird$Year==lavtyr & seabird$avgtemp==lavtmin]) - 0.5
     lavtband2   <- (seabird$latitude[seabird$depth=="Shallow" & seabird$Year==lavtyr & seabird$avgtemp==lavtmin]) + 0.5
     
     lavtmax     <- max(seabird$avgtemp[seabird$depth=="Shallow"])
     lavtyrmx    <- (seabird$Year[seabird$depth=="Shallow" & seabird$avgtemp==lavtmax])
     lavtband1mx <- (seabird$latitude[seabird$depth=="Shallow" & seabird$Year==lavtyrmx & seabird$avgtemp==lavtmax]) - 0.5
     lavtband2mx <- (seabird$latitude[seabird$depth=="Shallow" & seabird$Year==lavtyrmx & seabird$avgtemp==lavtmax]) + 0.5
     
     mavt        <- min(seabird$avgtemp[seabird$depth  == "Mid"])
     mavtyr      <- (seabird$Year[seabird$depth  == "Mid" & seabird$avgtemp  == mavt])
     mavtband1   <- (seabird$latitude[seabird$depth == "Mid" & seabird$Year==mavtyr & seabird$avgtemp  == mavt]) - 0.5
     mavtband2   <- (seabird$latitude[seabird$depth == "Mid" & seabird$Year==mavtyr & seabird$avgtemp  == mavt]) + 0.5
     
     mavtmx      <-  max(seabird$avgtemp[seabird$depth  == "Mid"])
     mavtyrmx    <- (seabird$Year[seabird$depth  == "Mid" & seabird$avgtemp  == mavtmx])
     mavtband1mx <- (seabird$latitude[seabird$depth == "Mid" & seabird$Year==mavtyrmx & seabird$avgtemp  == mavtmx]) - 0.5
     mavtband2mx <- (seabird$latitude[seabird$depth == "Mid" & seabird$Year==mavtyrmx & seabird$avgtemp  == mavtmx]) + 0.5
     
     davt        <-  min(seabird$avgtemp[seabird$depth  == "Deep"])
     davtyr      <- (seabird$Year[seabird$depth  == "Deep" & seabird$avgtemp  == davt])
     davtband1   <- (seabird$latitude[seabird$depth == "Deep" & seabird$Year==davtyr & seabird$avgtemp  == davt]) - 0.5
     davtband2   <- (seabird$latitude[seabird$depth == "Deep" & seabird$Year==davtyr & seabird$avgtemp  == davt]) + 0.5  
     
     davtmx      <-  max(seabird$avgtemp[seabird$depth  == "Deep"])
     davtyrmx    <- (seabird$Year[seabird$depth  == "Deep" & seabird$avgtemp  == davtmx])
     davtband1mx <- (seabird$latitude[seabird$depth == "Deep" & seabird$Year==davtyrmx & seabird$avgtemp  == davtmx]) - 0.5
     davtband2mx <- (seabird$latitude[seabird$depth == "Deep" & seabird$Year==davtyrmx & seabird$avgtemp  == davtmx]) + 0.5
     
```


## OCEANOGRAPHIC TEMPERATURES AND DEPTHS
Co-plots of average temperatures and average depths by 1-degree latitude intervals from south-west Vancouver Island to northwest Haida Gwaii can be found in Figure \@ref(fig:figure17).  The `r yr` survey data exhibit a general trend of decreasing temperature with depth. 

SBE 39 recorders have been placed on survey fishing sets since 2006. In the shallow waters, the lowest average temperature was `r round(lavtmin,1)` $^\circ$C (`r lavtyr`) within the `r lavtband1`$^\circ$- `r lavtband2`$^\circ$ latitude band.  The highest average temperature was `r round(lavtmax,1)` $^\circ$C (`r lavtyrmx`) in the southern `r lavtband1mx`$^\circ$ - `r lavtband2mx`$^\circ$ latitude band. Moving into the mid-depth waters, from 458-823 meters, the lowest average temperature was `r round(mavt,1)` $^\circ$C (`r mavtyr`) within the `r mavtband1`$^\circ$-`r mavtband2` $^\circ$ latitude band.  The highest average temperature was `r round(mavtmx,1)` $^\circ$C (`r mavtyrmx`) in the southern `r mavtband1mx`$^\circ$- `r mavtband2mx`$^\circ$ latitude band.  In the deepest waters, the lowest average temperature of `r round(davt,1)` $^\circ$C  (`r davtyr`) was found in the `r davtband1`$^\circ$- `r davtband2`$^\circ$ latitude band and the highest average temperature was `r round(davtmx,1)`$^\circ$C (`r davtyrmx`) in the southern `r davtband1mx`$^\circ$-`r davtband2mx`$^\circ$ latitude band (Figure \@ref(fig:figure18)).


```{r acknowledge, echo=FALSE}

    names      <-  paste(" select keyid, Association, year, Names from dbo.ReportSurvey_Acknowlegdements where year=", yr+1, sep="")
    credits    <-  GetSQLData(names,"Sablefish")
    write.table(credits, file = paste(path,"results13.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    credits    <-  read.csv(paste(path,'results13.csv',sep=''),header=T) 
    
```    
                                                                                                        
## ACKNOWLEDGEMENTS

The stock assessment survey and data report is the result of the collaborative efforts of many individuals.  Wild Canadian Sablefish has provided coordination and support of the annual Sablefish survey since 1994.  The scientific staff that conducted the `r yr` sablefish research charter included `r credits[1,4]` of Archipelago Marine Research Ltd (AMR).  A special thanks to the skipper and crew of the F/V `r boat`, whose efforts made the survey successful.  In `r yr`, the crew consisted of `r credits[2,4]`.


\clearpage


