# Tables
(ref:Table1Caption) Spatial strata allocation and completed strata counts (blue) for the `r yr` sablefish research and assessment survey.

```{r table1, echo=FALSE}

       Strata      <- c("S1 (South West Coast Vancouver Island or SWCVI)",
                        "S2 (North West Coast Vancouver Island or NWCVI)",
                        "S3 (Queen Charlotte Sound or QCS)",
                        "S4 (South West Coast Haida Gwaii or SWCHG)",
                        "S5 (North West Coast Haida Gwaii or NWCHG)",
                        "Total ")
       act.strata  <- paste("select Year, DEPTH_STRATUM, SPATIAL_STRATUM, COUNT([SET]) AS sets ",
                           "from dbo.GFBIO_RESEARCH_TRIPS ",
                           "group by Year, DEPTH_STRATUM, SPATIAL_STRATUM ",
                           "having (Year = ", yr, " )", sep="")
       #surv.strata <- GetSQLData(act.strata,"Sablefish")
       #write.table(surv.strata, file = paste(path,"Table1.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
       surv.strata <-  read.csv(paste(path,'table1.csv',sep=''), header=T)

       RD1      <- c(6,6,8,6,6,32)
       RD1fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD1"]
       RD1fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD1"])
       RD2fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD2"]
       RD2fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD2"])
       RD3fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD3"]
       RD3fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD3"])     
       RD2      <- c(8,7,6,6,7,34)
       RD3      <- c(5,5,5,5,5,25)
       Total    <- c(19,18,19,17,18,91)
       Totfish  <- c(RD1fish[1]+RD2fish[1]+RD3fish[1], RD1fish[2]+RD2fish[2]+RD3fish[2],
                     RD1fish[3]+RD2fish[3]+RD3fish[3], RD1fish[4]+RD2fish[4]+RD3fish[4],
                     RD1fish[5]+RD2fish[5]+RD3fish[5], RD1fish[6]+RD2fish[6]+RD3fish[6]) # addition
       dataf    <- data.frame(Strata, RD1, RD1fish, RD2, RD2fish,RD3, RD3fish, Total, Totfish) 
       yrRD1    <- paste("RD1 ",yr,sep="")
       yrRD2    <- paste("RD2 ",yr,sep="")
       yrRD3    <- paste("RD3 ",yr,sep="")
       yrTot    <- paste("Total ",yr,sep="")
       
       colnames(dataf) <- c("Spatia Strata", "RD1",yrRD1, "RD2",yrRD2,"RD3",yrRD3,"Total",yrTot)
   
       kableExtra::kable(dataf, booktabs = TRUE,linesep = "",
                   format = "latex",
                   caption = "(ref:Table1Caption)") %>%
              row_spec(0,    bold = T) %>%
              row_spec(5, hline_after = T) %>%
              column_spec(2, width  = "0.5cm") %>%
              column_spec(3, width  = "0.5cm", color="blue" ) %>%
              column_spec(4, width  = "0.5cm") %>%
              column_spec(5, width  = "0.5cm", color="blue") %>% 
              column_spec(6, width  = "0.5cm") %>% 
              column_spec(7, width  = "0.5cm", color="blue") %>%          
              column_spec(8, width  = "0.7cm") %>%
              column_spec(9, width  = "0.5cm", color="blue") %>% 
              row_spec(0, color="black") %>%
              row_spec(6, bold=T) %>%
              add_header_above(c(" "= 1, "Depth Strata" = 6, " " = 2), bold=T) %>%
       kableExtra::kable_styling(font_size = 10, position = "left",latex_options = "hold_position")
  
  
```

(ref:Table2Caption) Summary of species captured during the `r yr` survey StRS sets conducted by the `r boat`. No value in the weight column indicates that the catch was not weighed. No value in both weight and count indicates trace weights of less than 1 kg recorded.


```{r table2,  echo=FALSE}

    options(knitr.kable.NA = '')
    dtSP   <- paste("exec procRReport_SpeciesSummary ",yr," ,'StRS'",sep="")
    #datSP  <- GetSQLData(dtSP,"Sablefish")
    #write.table(datSP, file = paste(path,"Table2.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
    datSP  <-  read.csv(paste(path,'table2.csv',sep=''), header=T)
       
    dat1SP <- datSP[,c(-1)] 
    dat1SP <- dat1SP[,c(-3)]
    dat1SP <- dat1SP[,c(-2)]
    dat1SP <- dat1SP[,c(-6)]  # trim columns
    cleandataSP<-dat1SP
    cleandataSP$Summary_sp <- cleanf(cleandataSP$Summary_sp)  #  remove duplicates function
    colnames(cleandataSP)  <- c( "Category", "Common Name", "Scientific Name" , "Count", "Weight(kg)")
    
    kableExtra::kable(cleandataSP,
                      booktabs = TRUE,linesep = "",
                      format = "latex",  caption = "(ref:Table2Caption)") %>%
                      row_spec(0,    bold = T) %>%
                      row_spec(10,  hline_after = T) %>%
                      row_spec(17,  hline_after = T) %>%
                      row_spec(21,  hline_after = T) %>%
                      kableExtra::kable_styling(font_size = 8, position = "left",
                                                latex_options = "hold_position")
```


(ref:Table3Caption) Summary of sablefish fork length measurements collected during the `r yr` stratified random sets by spatial and depth stratum.

```{r table3, echo=FALSE}

    #newdata2   <-   rbind(newdata,biosumm)
    newdata2    <-   newdata  # created in results section

    kableExtra::kable(newdata2, row.names = FALSE,
                booktabs = TRUE,   linesep = "",
                format = "latex",  caption = "(ref:Table3Caption)") %>% 
    add_header_above(c("Depth Strata/Locality"= 2,
                        "Proportion" = 2, 
                        "Mean Fork Length (mm)" = 3),bold=T) %>%
      
    kableExtra::kable_styling(font_size = 9, position = "left", latex_options = "hold_position") %>%
                row_spec(0,    bold = T) %>%
                row_spec(3,    hline_after = T) %>%
                row_spec(4,    bold = T, hline_after = T) %>%
                row_spec(7,    hline_after = T) %>% 
                row_spec(8,    bold = T, hline_after = T) %>%      
                row_spec(11,   hline_after = T) %>%
                row_spec(12,   bold = T, hline_after = T) %>%      
                row_spec(15,   hline_after = T)   %>% 
                row_spec(16,   bold = T, hline_after = T) %>%   
                row_spec(19,   hline_after = T)   %>% 
                row_spec(20,   bold = T)
      
```

(ref:Table4Caption) Sablefish tag recovery counts by distance from release site and years at liberty before re-release for the 2020 survey. Distances were determined using the great circle distance between the survey release location and survey recovery location.


```{r table4, echo=FALSE}

       # in('A00545713','A00984002','A00254854') 3 tags re-released twice
       # in('A00733036','A00315966','A00550705')
      # in('A00545713','A00984002','A00254854','A00733036','A00315966','A00550705') 

      tag  <- paste("select * from Report_Survey_Tag_Recoveries",sep="") # have to go in database and change the year value
      #tag.rec <- GetSQLData(tag,"FishTag")
      #write.table(tag.rec, file = paste(path,"table4.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
      tag.rec <-  read.csv(paste(path,'table4.csv',sep=''), header=T)
      
      tag.rec[is.na(tag.rec)] <- 0   # convert NA to zero in whole table
      tag.rec$YearGroups      <- as.character(tag.rec$YearGroups)  # change column to character
      tag.rec$YearGroups      <- gsub("Grp1.", "", tag.rec$YearGroups)
      tag.rec$YearGroups      <- gsub("Grp2.", "", tag.rec$YearGroups)
      tag.rec$YearGroups      <- gsub("Grp3.", "", tag.rec$YearGroups)  
      tag.rec$YearGroups      <- gsub("Grp4.", "", tag.rec$YearGroups)      
      tag.rec$Recoveries      <- as.numeric(rowSums(tag.rec[,2:8], na.rm=TRUE))
      
      ad.row <- c('Total Counts',sum(tag.rec$X.10.km),sum(tag.rec$X11.50.km),sum(tag.rec$X51.100.km),
                          sum(tag.rec$X101.250.km),sum(tag.rec$X251.500.km),sum(tag.rec$X501.1000.km),
                          sum(tag.rec$X.1000.km), sum(tag.rec$Recoveries) )
      tag.rec2 <- rbind(tag.rec,ad.row) 

      names(tag.rec2) <- c("Years at Liberty","<10","11-50","51-100","101-250","251-500","501-1000","1000+","Recovery count")
   
      kableExtra::kable(tag.rec2, row.names = FALSE,
                booktabs = TRUE,   linesep = "",
                format = "latex",  caption = "(ref:Table4Caption)") %>% 
      add_header_above(c(" "= 1,
                        "Distance (km) from Release Location" = 7, 
                        " " = 1),bold=T) %>% 
      
       kableExtra::kable_styling(font_size = 9, position = "left", latex_options = "hold_position") %>%
                row_spec(0,    bold = T) %>%
                row_spec(4, hline_after = T) %>%
                column_spec(2, width  = "1.1cm") 

```
\clearpage
(ref:Table5Caption) Tag history of the events of three previously tagged sablefish recovered on the 2020 survey.

```{r table5, echo=FALSE}

      GIS1 <- paste("SELECT  get_tags3.TAG_ID, CONVERT(varchar, FISH_TAG_EVENTS_4.EVENT_DATE, 101) AS date1, FISH_TAG_EVENTS_4.EVENT_YEAR, dbo.EVENT_TYPE.EVENT_DESCRIPTION, FISH_TAG_EVENTS_4.EVENT_NUMBER, FISH_TAG_EVENTS_4.EVENT_TRIP,  dbo.FISH_STATE.RECOVERY_STATE_DESC, dbo.q_Fish_Tag_Lengths.Length, FISH_TAG_EVENTS_4.TAG_NUMBER,  FISH_TAG_EVENTS_4.PREVIOUS_TAG_NUMBER, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,FISH_TAG_EVENTS_4.EVENT_SET,FISH_TAG_EVENTS_4.RECAPTURE_FISH_ID FROM  dbo.EVENT_TYPE RIGHT OUTER JOIN  (SELECT  TAG_ID, rfi   FROM   (SELECT   FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi  FROM   (SELECT  TAG_ID, CASE WHEN RECAPTURE_FISH_ID = 0 THEN - 99 ELSE ISNULL(RECAPTURE_FISH_ID, - 99) END AS rfi FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM   dbo.FISH_TAG_EVENTS WHERE  (TAG_NUMBER = N'A00315966')) AS QRY1 UNION  SELECT   TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00315966')) AS QRY2) AS QRY3 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3.rfi = FISH_TAG_EVENTS_1.RECAPTURE_FISH_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi HAVING  (QRY3.rfi IS NOT NULL)) AS get_tags1  UNION SELECT  TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT  FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID FROM (SELECT TAG_ID, RECAPTURE_FISH_ID FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_3 WHERE    (TAG_NUMBER = N'A00315966')) AS QRY1_1 UNION SELECT   TAG_ID, RECAPTURE_FISH_ID   FROM   (SELECT     TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00315966')) AS QRY2_1) AS QRY3_1 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3_1.TAG_ID = FISH_TAG_EVENTS_1.TAG_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID  HAVING (QRY3_1.RECAPTURE_FISH_ID IS NULL)) AS get_tags2) AS get_tags3 INNER JOIN  dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_4 ON get_tags3.TAG_ID = FISH_TAG_EVENTS_4.TAG_ID ON dbo.EVENT_TYPE.EVENT_TYPE = FISH_TAG_EVENTS_4.EVENT_TYPE LEFT OUTER JOIN dbo.FISH_STATE RIGHT OUTER JOIN dbo.FISH_TAG_REC_SPECS ON dbo.FISH_STATE.RECOVERY_STATE_CODE = dbo.FISH_TAG_REC_SPECS.RECOVERY_STATE ON FISH_TAG_EVENTS_4.TAG_ID = dbo.FISH_TAG_REC_SPECS.TAG_ID LEFT OUTER JOIN dbo.q_Fish_Tag_Lengths ON FISH_TAG_EVENTS_4.TAG_ID = dbo.q_Fish_Tag_Lengths.TAG_ID ORDER BY FISH_TAG_EVENTS_4.EVENT_YEAR, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,date1 ", sep="")   # for 2020 only
 GIS2 <- paste("SELECT  get_tags3.TAG_ID, CONVERT(varchar, FISH_TAG_EVENTS_4.EVENT_DATE, 101) AS date1, FISH_TAG_EVENTS_4.EVENT_YEAR, dbo.EVENT_TYPE.EVENT_DESCRIPTION, FISH_TAG_EVENTS_4.EVENT_NUMBER, FISH_TAG_EVENTS_4.EVENT_TRIP,  dbo.FISH_STATE.RECOVERY_STATE_DESC, dbo.q_Fish_Tag_Lengths.Length, FISH_TAG_EVENTS_4.TAG_NUMBER,  FISH_TAG_EVENTS_4.PREVIOUS_TAG_NUMBER, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,FISH_TAG_EVENTS_4.EVENT_SET,FISH_TAG_EVENTS_4.RECAPTURE_FISH_ID FROM  dbo.EVENT_TYPE RIGHT OUTER JOIN  (SELECT  TAG_ID, rfi   FROM   (SELECT   FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi  FROM   (SELECT  TAG_ID, CASE WHEN RECAPTURE_FISH_ID = 0 THEN - 99 ELSE ISNULL(RECAPTURE_FISH_ID, - 99) END AS rfi FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM   dbo.FISH_TAG_EVENTS WHERE  (TAG_NUMBER = N'A00550705')) AS QRY1 UNION  SELECT   TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00550705')) AS QRY2) AS QRY3 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3.rfi = FISH_TAG_EVENTS_1.RECAPTURE_FISH_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi HAVING  (QRY3.rfi IS NOT NULL)) AS get_tags1  UNION SELECT  TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT  FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID FROM (SELECT TAG_ID, RECAPTURE_FISH_ID FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_3 WHERE    (TAG_NUMBER = N'A00550705')) AS QRY1_1 UNION SELECT   TAG_ID, RECAPTURE_FISH_ID   FROM   (SELECT     TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00550705')) AS QRY2_1) AS QRY3_1 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3_1.TAG_ID = FISH_TAG_EVENTS_1.TAG_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID  HAVING (QRY3_1.RECAPTURE_FISH_ID IS NULL)) AS get_tags2) AS get_tags3 INNER JOIN  dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_4 ON get_tags3.TAG_ID = FISH_TAG_EVENTS_4.TAG_ID ON dbo.EVENT_TYPE.EVENT_TYPE = FISH_TAG_EVENTS_4.EVENT_TYPE LEFT OUTER JOIN dbo.FISH_STATE RIGHT OUTER JOIN dbo.FISH_TAG_REC_SPECS ON dbo.FISH_STATE.RECOVERY_STATE_CODE = dbo.FISH_TAG_REC_SPECS.RECOVERY_STATE ON FISH_TAG_EVENTS_4.TAG_ID = dbo.FISH_TAG_REC_SPECS.TAG_ID LEFT OUTER JOIN dbo.q_Fish_Tag_Lengths ON FISH_TAG_EVENTS_4.TAG_ID = dbo.q_Fish_Tag_Lengths.TAG_ID ORDER BY FISH_TAG_EVENTS_4.EVENT_YEAR, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,date1 ", sep="")   # for 2020 only
GIS3 <- paste("SELECT  get_tags3.TAG_ID, CONVERT(varchar, FISH_TAG_EVENTS_4.EVENT_DATE, 101) AS date1, FISH_TAG_EVENTS_4.EVENT_YEAR, dbo.EVENT_TYPE.EVENT_DESCRIPTION, FISH_TAG_EVENTS_4.EVENT_NUMBER, FISH_TAG_EVENTS_4.EVENT_TRIP,  dbo.FISH_STATE.RECOVERY_STATE_DESC, dbo.q_Fish_Tag_Lengths.Length, FISH_TAG_EVENTS_4.TAG_NUMBER,  FISH_TAG_EVENTS_4.PREVIOUS_TAG_NUMBER, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,FISH_TAG_EVENTS_4.EVENT_SET,FISH_TAG_EVENTS_4.RECAPTURE_FISH_ID FROM  dbo.EVENT_TYPE RIGHT OUTER JOIN  (SELECT  TAG_ID, rfi   FROM   (SELECT   FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi  FROM   (SELECT  TAG_ID, CASE WHEN RECAPTURE_FISH_ID = 0 THEN - 99 ELSE ISNULL(RECAPTURE_FISH_ID, - 99) END AS rfi FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM   dbo.FISH_TAG_EVENTS WHERE  (TAG_NUMBER = N'A00733036')) AS QRY1 UNION  SELECT   TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT   TAG_ID, RECAPTURE_FISH_ID  FROM dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00733036')) AS QRY2) AS QRY3 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3.rfi = FISH_TAG_EVENTS_1.RECAPTURE_FISH_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3.rfi HAVING  (QRY3.rfi IS NOT NULL)) AS get_tags1  UNION SELECT  TAG_ID, RECAPTURE_FISH_ID FROM    (SELECT  FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID FROM (SELECT TAG_ID, RECAPTURE_FISH_ID FROM   (SELECT   TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_3 WHERE    (TAG_NUMBER = N'A00733036')) AS QRY1_1 UNION SELECT   TAG_ID, RECAPTURE_FISH_ID   FROM   (SELECT     TAG_ID, RECAPTURE_FISH_ID FROM   dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_2 WHERE  (PREVIOUS_TAG_NUMBER = N'A00733036')) AS QRY2_1) AS QRY3_1 INNER JOIN dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_1 ON QRY3_1.TAG_ID = FISH_TAG_EVENTS_1.TAG_ID GROUP BY FISH_TAG_EVENTS_1.TAG_ID, QRY3_1.RECAPTURE_FISH_ID  HAVING (QRY3_1.RECAPTURE_FISH_ID IS NULL)) AS get_tags2) AS get_tags3 INNER JOIN  dbo.FISH_TAG_EVENTS AS FISH_TAG_EVENTS_4 ON get_tags3.TAG_ID = FISH_TAG_EVENTS_4.TAG_ID ON dbo.EVENT_TYPE.EVENT_TYPE = FISH_TAG_EVENTS_4.EVENT_TYPE LEFT OUTER JOIN dbo.FISH_STATE RIGHT OUTER JOIN dbo.FISH_TAG_REC_SPECS ON dbo.FISH_STATE.RECOVERY_STATE_CODE = dbo.FISH_TAG_REC_SPECS.RECOVERY_STATE ON FISH_TAG_EVENTS_4.TAG_ID = dbo.FISH_TAG_REC_SPECS.TAG_ID LEFT OUTER JOIN dbo.q_Fish_Tag_Lengths ON FISH_TAG_EVENTS_4.TAG_ID = dbo.q_Fish_Tag_Lengths.TAG_ID ORDER BY FISH_TAG_EVENTS_4.EVENT_YEAR, FISH_TAG_EVENTS_4.FISH_EVENT_NUMBER,date1 ", sep="")   # for 2020 only
      
      
      #GIS1.tag.rec <- GetSQLData(GIS1,"FishTag")
      #GIS2.tag.rec <- GetSQLData(GIS2,"FishTag")
      #GIS3.tag.rec <- GetSQLData(GIS3,"FishTag")
      #GIS.tag.rec  <- rbind(GIS2.tag.rec, GIS1.tag.rec, GIS3.tag.rec)
      #write.table(GIS.tag.rec, file = paste(path,"table4b.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
      GIS.tag.rec <-  read.csv(paste(path,'table4b.csv',sep=''), header=T)
      GIS.tag.rec <-  GIS.tag.rec[,c(-1,-11,-13)]
      GIS.tag.rec$RECOVERY_STATE_DESC <- " LIVE, RE-RELEASED"
      GIS.tag.rec2 <-  GIS.tag.rec[ , c("TAG_NUMBER", "PREVIOUS_TAG_NUMBER", "EVENT_DESCRIPTION","EVENT_NUMBER", "EVENT_TRIP","EVENT_SET","EVENT_YEAR",
                                        "date1","RECOVERY_STATE_DESC", "Length")]
      
      names(GIS.tag.rec2) <-   c("Release Tag number", "Previous Tag number", "Event","Event no.","Event Trip","Event Set","Event year",
                                 "Date","Fish State", "Length (mm)")
      GIS.tag.rec2 <- GIS.tag.rec2[GIS.tag.rec2$Event=='RELEASE',]
      
 
      kableExtra::kable(GIS.tag.rec2, row.names = FALSE,
                booktabs = TRUE,   linesep = "",
                format = "latex",  caption = "(ref:Table5Caption)") %>% 
 
       kableExtra::kable_styling(font_size = 9, position = "left", latex_options = "hold_position") %>%
                row_spec(0,    bold = T) %>%
                row_spec(3, hline_after = T) %>%
                row_spec(6, hline_after = T) %>%
                column_spec(1, width  = "1.7cm")  %>%
                column_spec(2, width  = "1.7cm")  %>%
                column_spec(3, width  = "1.1cm")  %>%
                column_spec(4, width  = "0.7cm")  %>%
                column_spec(5, width  = "0.7cm")  %>%
                column_spec(6, width  = "0.7cm")  %>%  
                column_spec(7, width  = "0.7cm")  %>% 
                column_spec(8, width  = "0.7cm")  %>%   
                column_spec(8, width  = "1.3cm")  %>%  
                column_spec(9, width  = "3.2cm")  %>%  
                column_spec(10, width  = "0.7cm")          
```


\clearpage

