<!-- The following code should appear at the beginning of the first appendix.
(if you have one)
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# LIST OF SABLEFISH RESEARCH AND ASSESSMENT SURVEYS. {#app:first-appendix}

```{r appendixA, results="asis"}

   dtBW   <- paste('exec dbo.procRKnitr_SurveyTrips ', yr ,sep='')
   #trip   <- GetSQLData(dtBW,"Sablefish")
   #write.table(trip, file = paste(path,'appendixA.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   trip   <-  read.csv(paste(path,'appendixA.csv',sep=''),header=T)
   
   colnames(trip) <- c("Year", "Dates",  "Vessel", "Captain", "Set Count", "GFBIO Id")
   kableExtra::kable(trip,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     format = "latex")  %>%
   kableExtra::kable_styling(font_size = 8) %>% 
                     row_spec(0, bold = T)

```

\clearpage

# DATA FORMS OF THE 2020 SABLEFISH SURVEY. {#app:second-appendix}

```{r appendixB,out.width = "480px", out.height = "406px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper bridge log
         img <-  paste(basepath,'figures/AppendixB_BridgeLogIns3.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure B.1. Example of a completed bridge log data form with directions from the 2020 survey instruction manual.

\clearpage

```{r AppendixB2,out.width = "500px", out.height = "420px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper set log
         img <-  paste(basepath,'figures/AppendixB_SetLogIns3.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure B.2.  Example of a completed set log data form with directions from the 2020 survey instruction manual.

\clearpage

```{r AppendixB3,out.width = "500px", out.height = "476px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper catch log
         img <-  paste(basepath,'figures/AppendixB_CatchLogIns3.png',sep='')
      knitr::include_graphics(img) 
      
```
Figure B.3.  Example of a completed catch log data form with directions from the 2020 survey instruction manual.
\clearpage

```{r AppendixB4,out.width = "500px", out.height = "426px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper tabular catch log
         img <-  paste(basepath,'figures/AppendixB_CatchLogTabIns3.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure B.4.  Example of a tabular catch log data entry form transposed from the catch log in Figure B.3. Directions from the 2020 survey instruction manual. 

\clearpage

```{r AppendixB5,out.width = "480px", out.height = "588px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper LSWMO log
         img <-  paste(basepath,'figures/AppendixB_LSWMOIns3.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure B.5.  Example of a completed Sablefish biological sampling form and directions from the 2020 survey instruction manual. 

\clearpage

```{r AppendixB6,out.width = "500px", out.height = "501px", fig.align="left"}

      if(knitr:::is_latex_output())
         # paper tagging sheet
         img <-  paste(basepath,'figures/AppendixB_TaggingSheetIns3.png',sep="")
      knitr::include_graphics(img) 
      
```


Figure B.6.  Example of a completed tagging form with directions from the 2020 survey instruction manual.

\clearpage

# SURVEY SET DETAILS `r yr`. {#app:third-appendix}
Details of sets completed during the `r yr` survey program (F/V `r boat`).  Sets are listed by stratum/inlet name, set type, depth stratum, start date, end of gear deployment time and duration in minutes. The depth strata for type 3 tagging sets include RD~1~ (100-250 fathoms), RD~2~ (250-450 fathoms) and RD~3~ (450-750 fathoms). The position data includes the major area and start and end latitude and longitude in degrees decimal minutes. The bottom depths (in meters) of the fishing set are shown with the mean bottom depth calculated from recordings at one minute intervals between the start and end of the set. The number of traps fished for each set excludes open traps, while holed or fouled traps have been included.  Sets that successfully deployed a Seabird SBE temperature and pressure recorder are indicated with an 'x'. 


```{r appendixC, results="asis"}
   library(kableExtra)
   yr <- 2020
   options(knitr.kable.NA = '')  # get rid of NAs
   srvyset  <-  paste('dbo.procRReport_Survey_SetDetails ',yr,',1,',setcnt, sep='')
   #srvy.set   <-  GetSQLData(srvyset,"Sablefish")
   #write.table(srvy.set, file = paste(path,'AppendixC.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   srvy.set <-  read.csv(paste(path,'AppendixC.csv',sep=''),header=T)
   
   latcnt  <-  length(srvy.set[, 9])  # add degree symbol in lat and long values
               for (i in 1:latcnt)
                      { srvy.set[i,9]= paste(srvy.set[i,9],'째 ', srvy.set[i,10],"'N",sep="")  }
   latcnt  <-  length(srvy.set[,11])
               for (i in 1:latcnt)
                      { srvy.set[i,11]=paste(srvy.set[i,11],'째 ', srvy.set[i,12],"'W",sep="") }
   latcnt  <-  length(srvy.set[,13])
               for (i in 1:latcnt)
                      { srvy.set[i,13]=paste(srvy.set[i,13],'째 ', srvy.set[i,14],"'N",sep="") }
   latcnt<-length(srvy.set[,15])
               for (i in 1:latcnt)
                      { srvy.set[i,15]=paste(srvy.set[i,15],'째 ', srvy.set[i,16],"'W",sep="") }
   
   srvy.set  <-  srvy.set[,c(-22,-23,-24)]  # no hobo, ctd or camera columns needed 2020
   srvy.set  <-  srvy.set[,c(-10,-12,-14,-16)]  
   
   colnames(srvy.set) <- c("Spatial Stratum", "Set", "Type",      
                           "Depth Stratum",   "Date", "Time", 
                           "Duration (minutes)",  "Area", 
                           "Start Latitude",  "Start Longitude", 
                           "End Latitude",    "End Longitude", 
                           "Start Depth (m)", "End Depth (m)", "Mean Depth (m)", 
                           "Traps Fished",    "SBE 39")
 
   kableExtra::kable(srvy.set,
                    booktabs  = TRUE, 
                    longtable = T,
                    linesep   = "",
                    escape = F,
                    format    = "latex") %>%
   kableExtra::kable_styling(font_size = 8, latex_options = "repeat_header",
               repeat_header_text = "continued.", 
               repeat_header_method = "replace") %>%
   kableExtra::landscape() %>%
    
   row_spec(0, bold = T)  %>%     
   column_spec(1,width    = "0.7cm") %>%  # stratum
   column_spec(2,width    = "0.5cm") %>%  # set
   column_spec(3,width    = "0.4cm") %>%  # type 
   column_spec(4,width    = "0.7cm") %>%  # depth stratum
   column_spec(5,width    = "0.9cm") %>%  # date
   column_spec(6,width    = "0.6cm") %>%  # time      
   column_spec(7,width    = "0.9cm") %>%  # dur
   column_spec(8,width    = "0.5cm") %>%  # area   
   column_spec(9,width    = "1.2cm") %>%  # start lat
   column_spec(10,width   = "1.7cm") %>%  # start long
   column_spec(11,width   = "1.2cm") %>%  # end lat
   column_spec(12,width   = "1.7cm") %>%  # end long
   column_spec(13,width   = "0.7cm") %>%  # start dep
   column_spec(14,width   = "0.7cm") %>%  # end dep    
   column_spec(15,width   = "0.5cm") %>%  # mean dep
   column_spec(16,width   = "0.6cm") %>%  # tf
   column_spec(17,width   = "0.4cm") %>%  # sbe
   sub("\\caption\\[\\]\\{\\}", "\\caption*{}", .)
``` 

\clearpage


# SUMMARY OF BASKET USE BY TRAP `r yr`.{#app:fourth-appendix} 

Summary of the basket use by trap number for StRS sets during the `r yr` sablefish survey. The fate of the sablefish catch for each set and trap is indicated using the following abbreviations: D = Discarded after weighing (processed as commercial catch), A = Sampled for LSMWO, T = Tagged and released, SD = Sublegal discarded, F= Frames, NULL = No sablefish catch/Trap missing. 

```{r appendixD, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

   # Sablefish.dbo.procRReport_Survey_TrapUse procedure pulls 
   # data from table dbo.GFBIO_TRAPS_USE  
   # created by procedure Sablefish.dbo.Build_BIO_Sablefish_Tables
   options(knitr.kable.NA = '')
   trap       <- paste("dbo.procRReport_Survey_TrapUse ",yr,",1,",setcnt, sep="")
   #trapdat    <- GetSQLData(trap,"Sablefish")
   #write.table(trapdat, file = paste(path,'appendixD.csv',sep=''),row.names=FALSE,na="",col.names=TRUE,sep=",")    
   trapdat    <- read.csv(paste(path,'appendixD.csv',sep=''),header=T)
   trapuse    <- trapdat[,c(-1)] 
   trapuse2   <- trapuse[,c(-27,-28)]
   
   kableExtra::kable(trapuse2,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     format = "latex")   %>%
      
   kableExtra::kable_styling(font_size = 6, 
                     latex_options = "repeat_header",
                     repeat_header_text = "continued.", 
                     repeat_header_method = "replace") %>%  
      
   kableExtra::landscape()  %>%
       #row_spec(38:52, color="blue"  ) %>%  no visits to inlets in 2020 
       row_spec(0, bold=T) %>%
       column_spec(1,width      = "0.3cm") %>%
       column_spec(2,width      = "0.3cm") %>%
       column_spec(3,width      = "0.3cm") %>%
       column_spec(4,width      = "0.3cm") %>%
       column_spec(5,width      = "0.3cm") %>%
       column_spec(6,width      = "0.3cm") %>%
       column_spec(7,width      = "0.3cm") %>%
       column_spec(8,width      = "0.3cm") %>%   
       column_spec(9,width      = "0.3cm") %>%   
       column_spec(10,width     = "0.3cm") %>%
       column_spec(11,width     = "0.4cm") %>%
       column_spec(12,width     = "0.4cm") %>%
       column_spec(13,width     = "0.4cm") %>%
       column_spec(14,width     = "0.4cm") %>%
       column_spec(15,width     = "0.4cm") %>%
       column_spec(16,width     = "0.4cm") %>%
       column_spec(17,width     = "0.4cm") %>%
       column_spec(18,width     = "0.4cm") %>%
       column_spec(19,width     = "0.4cm") %>%
       column_spec(20,width     = "0.4cm") %>%
       column_spec(21,width     = "0.4cm") %>%  
       column_spec(22,width     = "0.4cm") %>% 
       column_spec(23,width     = "0.4cm") %>%       
       column_spec(24,width     = "0.4cm") %>% 
       column_spec(25,width     = "0.4cm") %>%
       column_spec(26,width     = "0.4cm") %>%      
       column_spec(27,width     = "0.4cm") %>%  
       column_spec(28,width     = "0.4cm") 
```

\clearpage

```{r appendixESetUp, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
library(knitr)
library(dplyr)
library(pander)
library(ggplot2)


    trap.count <-paste("select tp.YEAR, fe.TRIP_ID, fe.FE_MAJOR_LEVEL_ID AS SET_ID, fe.FE_SUB_LEVEL_ID AS BECKET, ", 
                       "fe.FE_MINOR_LEVEL_ID AS TRAP, SUM(c.CATCH_COUNT) AS total_count ",
                       "from dbo.GFBIO_TRAP_VW_VW AS fe INNER JOIN ",
                       "(select YEAR, TRIP_ID from dbo.SURVEY_trips_vw ",
                       " group by YEAR, TRIP_ID) AS tp ON fe.TRIP_ID = tp.TRIP_ID LEFT OUTER JOIN ",
                       " GFBioSQL.dbo.TRAP_SPECS AS ts ON fe.FISHING_EVENT_ID = ts.FISHING_EVENT_ID LEFT OUTER JOIN ",
                       " (select FISHING_EVENT_ID, SUM(CASE WHEN BAIT_LURE_CODE = 15 AND BAIT_METHOD_CODE = 4  ",
                       " then TRPBL_BAIT_AMOUNT ELSE NULL END) AS BAGGED_SQUID, SUM(CASE WHEN BAIT_LURE_CODE = 18 and  ", 
                       " BAIT_METHOD_CODE = 6 THEN TRPBL_BAIT_AMOUNT ELSE NULL END) AS LOOSE_HAKE,  ",
                       " SUM(CASE WHEN (BAIT_LURE_CODE <> 15 AND BAIT_METHOD_CODE <> 4) AND (BAIT_LURE_CODE <> 18 AND  ",
                       " BAIT_METHOD_CODE <> 6) THEN TRPBL_BAIT_AMOUNT ELSE NULL END) AS OTHER_BAIT ",
                       " from GFBioSQL.dbo.TRAP_BAIT_LURE ",
                       " group by FISHING_EVENT_ID) AS bait ON fe.FISHING_EVENT_ID = bait.FISHING_EVENT_ID  ",
                       " LEFT OUTER JOIN ",
                       " (select fec.FISHING_EVENT_ID, GFBioSQL.dbo.CATCH.SPECIES_CODE,  ",
                       " SUM(GFBioSQL.dbo.CATCH.CATCH_WEIGHT) AS CATCH_WEIGHT, SUM(GFBioSQL.dbo.CATCH.CATCH_COUNT) AS CATCH_COUNT,  ",
                       " AVG(ISNULL(GFBioSQL.dbo.CATCH.CATCH_VERIFICATION_CODE, 0)) AS VERIFICATION_METHOD ",
                       " from GFBioSQL.dbo.FISHING_EVENT_CATCH AS fec INNER JOIN ",
                       " GFBioSQL.dbo.CATCH ON fec.CATCH_ID = GFBioSQL.dbo.CATCH.CATCH_ID ",
                       " where (GFBioSQL.dbo.CATCH.SPECIES_CODE = '455') ",
                       " GROUP BY fec.FISHING_EVENT_ID, GFBioSQL.dbo.CATCH.SPECIES_CODE) AS c ON fe.FISHING_EVENT_ID = c.FISHING_EVENT_ID ",
                       " GROUP BY fe.FE_MAJOR_LEVEL_ID, fe.TRIP_ID, tp.YEAR, fe.FE_SUB_LEVEL_ID, fe.FE_MINOR_LEVEL_ID",
                       " having  (tp.YEAR IN ('2020')) order by SET_ID, BECKET, TRAP",sep="")
    
   #trap.sable1   <- GetSQLData(trap.count,"Sablefish")
   #write.table(trap.sable1, file = paste(path,"appendixESetUp.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
   trap.sable1  <-  read.csv(paste(path,'appendixESetUp.csv',sep=''), header=T)


   library(tidyverse)
   library(tidyr)
   library(scales)
   
   trap.sable <- trap.sable1[,c(-1,-2,-4)] 
   #trap.sable$SET_ID <- as.factor(trap.sable$SET_ID)
   names(trap.sable) <- c("SurveySet","Trap","Value")
   trap.sable[is.na(trap.sable)] <- 0

   #  trap.sableTest  <-  trap.sable[trap.sable$SurveySet == 40,] 
   big.value <- max(trap.sable$Value)

   w<-trap.sable %>%
     group_by(SurveySet) %>%
     do({
       p <- ggplot(., aes(x = Trap, y = Value)) + 
         geom_area( fill="#6495ED", alpha=0.4) +   #6495ED
         geom_line(size = 4, color = "blue") +      
         #geom_point(size=15, color="red") + 
         ylim(0, big.value) +
         xlim(0,25) +
         theme_void() 
         #stat_summary(fun.y = max, colour = "red", geom = "point", size = 5)
       ggsave(p, filename = paste0("fig", unique(.$SurveySet), ".png"), width = 8, height = 1.9)  # save time comment out
       invisible(.) 
       
     })


```

# SUMMARY OF SABLEFISH BIOLOGICAL DATA `r yr`. {#app:fifth-appendix} 
Biological data collected for sablefish by set, catch weight in kilograms and numbers of fish.  Sablefish counts by trap are represented by sparklines. Tagged fish counts by number for recovered, re-released, deceased and those released for the first time. Tagged fish fork lengths are presented by count and mean (millimeters). Specimen counts are listed by sample type; mean fork lengths are tabulated.  


```{r appendixE, echo=FALSE}

   #  Sablefish.dbo.procReport_Survey_SampleDetails pulls data 
   #  from table GFBIO_RESEARCH_SAMPLE_DETAILS, built by     
   #  procedure Sablefish.dbo.Build_BIO_Sablefish_Tables 
   # \renewcommand{\arraystretch}{1} # use above r code to stretch table

   samples           <-  paste("dbo.procReport_Survey_SampleDetails ",yr,",1,",setcnt, sep="")
   #surveyspec        <-  GetSQLData(samples,"Sablefish")
   #write.table(surveyspec, file = paste(path,'appendixE.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   surveyspec        <-  read.csv(paste(path,'appendixE.csv',sep=''),header=T)
   count.row.total   <-  length(surveyspec$SET)
   count.row         <-  length(surveyspec$SET) - 1
   surveyspec$SET[count.row.total] <- "Total"
   
   surveyspec <-  surveyspec %>%
                  mutate(Sparkline = paste0("\\raisebox{.10\\height} {\\includegraphics[width=2cm]{fig",SET,".png}}") ) 
   
   colnames(surveyspec) <- c("", "kg","Count","Recover-Rerelease", "Deceased", "Released", 
                             "Count", "Mean", "Fork Length", "Sex","Maturity", "Otoliths",
                             "Weight","Count","Proportion Males", "Males", "Females", "Count by Trap")
   
   surveyspec <-  surveyspec[, c(1, 2, 3, 18, 4,5,6,7,8,9,10,11,12,13,14,15,16,17)]  #reorder table
   
   colnames(surveyspec) <- c("", "kg","Count","Count by Trap","Recover-Rerelease", "Deceased", "Released", 
                             "Count", "Mean", "Fork Length", "Sex","Maturity", "Otoliths",
                             "Weight","Count","Proportion Males", "Males", "Females" )

   kableExtra::kable(surveyspec,
                     booktabs = TRUE,     
                     longtable = T,
                     escape = F,        # lets the image show up 
                     linesep   = "",
                     align=rep('r', 18),
                     format = "latex") %>%
      
   add_header_above(c("Set"= 1,
                      "Total Catch" = 3, 
                      "Tagged Fish Counts" = 3,  
                      "Tagged Fork Lengths(mm)" = 2,
                      "Specimen Count"= 6, 
                      "Mean Fork Length(mm)" = 3), bold = TRUE) %>%
      
   kableExtra::kable_styling(font_size = 8, 
                     latex_options = "repeat_header",
                     repeat_header_text = "continued.", 
                     repeat_header_method = "replace") %>%     
   
   kableExtra::landscape()  %>%
   row_spec(0, bold = T)  %>%   
   column_spec(1,width    = "0.3cm") %>%  # set
   column_spec(2,width    = "0.6cm") %>%  # kg
   column_spec(3,width    = "0.7cm") %>%  # count
   column_spec(4,width    = "1.4cm") %>%  # sparkline      
   column_spec(5,width    = "0.9cm") %>%  # rr
   column_spec(6,width    = "1.0cm") %>%  # decease
   column_spec(7,width    = "0.9cm") %>%  # rel     
   column_spec(8,width    = "1.5cm") %>%  # count
   column_spec(9,width    = "0.9cm") %>%  # mean
   column_spec(10,width   = "0.7cm") %>%  # fl
   column_spec(11,width   = "0.6cm") %>%  # sex
   column_spec(12,width   = "0.7cm") %>%  # mat
   column_spec(13,width   = "0.7cm") %>%  # oto 
   column_spec(14,width   = "0.6cm") %>%  # wt
   column_spec(15,width   = "0.6cm") %>%  # cnt
   column_spec(16,width   = "1.1cm") %>%  # prop m
   column_spec(17,width   = "0.7cm") %>%  # male         
   column_spec(18,width   = "0.7cm") %>%  # fem
   row_spec(count.row.total, bold = T) %>%      
   row_spec(count.row,  hline_after = T) 
   
```
\clearpage

# SUMMARY OF BIOLOGICAL DATA FOR ROUGHEYE/BLACKSPOTTED ROCKFISH COMPLEX. {#app:sixth-appendix} 
Biological data collected for rougheye/blackspotted rockfish complex.  Each set is listed with counts of specimens sampled, calculations of mean fork lengths and number of species visually identified as either a RE = rougheye rockfish, BS = blackspotted rockfish or a hybrid.
\ \
\ \

```{r appendixF, echo=FALSE}
 
   othersamples <-  paste( "select species_name, [SET], [Len Sample Count], ",
                           "[weight_count], [Sex Sample Count], ",
                           "[Maturity Sample Count], [Otolith Sample Count], [DNA Sample Count], ",
                           "Sample_count, [Proportion Males],  ",   
                           "round([Male Mean Fork Len(mm)],0) as malelen, ",
                           "round([Female Mean Fork Len(mm)],0) as femlen,  ", 
                           "round([NoSexMeanLen(mm)],0) as nosexlen, ", 
                           "bsre.Rougheye, bsre.Blackspotted, bsre.Hybrid ",
                           "from  ",
                           "(select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "SUM(re) AS Rougheye, SUM(bs) AS Blackspotted, SUM(hyb) AS Hybrid ",
                           "from  (select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 16 THEN 1 ELSE 0 END AS re, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 17 THEN 1 ELSE 0 END AS bs, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 31 THEN 1 ELSE 0 END AS hyb, ",
                           "SPECIMEN_ID ",
                           "from dbo.gfbio_species_guess) AS bs ",
                           "group by year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE) AS bsre ", 
                           "RIGHT OUTER JOIN ",
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ON bsre.TRIP_ID = ",              
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.TRIP_ID and ",
                           "bsre.FE_MAJOR_LEVEL_ID = dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.[SET] ",
                           "and bsre.SPECIES_CODE = ",                       
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.species ",            
                           "where (dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.Year = ",yr, 
                           ") order by species,[SET]", sep="")
   #otherspec2            <-  GetSQLData(othersamples,"Sablefish")   # read from SQL Server
   #write.table(otherspec2, file = paste(path,'appendixF.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   otherspec2              <-  read.csv(paste(path,'appendixF.csv',sep=''),header=T) # read from csv
   otherspec2$species_name <-  as.character(otherspec2$species_name)
   otherspec2$species_name <-  gsub('ROUGHEYE/BLACKSPOTTED ROCKFISH COMPLEX', 'ROUGHEYE/ BLACKSPOTTED ROCKFISH COMPLEX', otherspec2$species_name)
   addition                <-  c('Total','', sum(otherspec2$Len.Sample.Count),    sum(otherspec2$weight_count), 
                                           sum(otherspec2$Sex.Sample.Count),    sum(otherspec2$Maturity.Sample.Count),   
                                           sum(otherspec2$Otolith.Sample.Count),sum(otherspec2$DNA.Sample.Count),
                                           sum(otherspec2$Sample_count),'','','','',sum(otherspec2$'Rougheye'),sum(otherspec2$'Blackspotted'),sum(otherspec2$'Hybrid'))
   otherspec             <-  rbind(otherspec2,addition)
   row.count             <-  length(otherspec$species_name)
  
   otherspec$species_name<-  cleanf(otherspec$species_name)    # only rougheye/blackspotted sampled in 2020
   colnames(otherspec)   <-  c("Species Name", "Set", "Fork Length",
                               "Weight", "Sex","Maturity", "Otolith", 
                               "DNA", "Total Count", 
                               "Proportion Males", "Males", "Females",  
                               "No sex", "RE", "BS","Hybrid" )
   
      kableExtra::kable(otherspec,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     align=c('l', 'r','c','c','c','c','c','c','c','c','c','c','c','c','c','c'),
                     format = "latex") %>%
      
      add_header_above(c(" "= 2,
                      "Specimen Count"= 7, 
                      "Mean Fork Length(mm)" = 4,
                      "Sampler Visual id Count" = 3), bold=TRUE) %>%
   
      kableExtra::kable_styling(font_size = 8, 
                        latex_options = "repeat_header",
                        repeat_header_text = "continued.", 
                        repeat_header_method = "replace") %>%
      
      kableExtra::landscape()  %>% 
         
      column_spec(1,width     = "3.5cm") %>% # species
      column_spec(2,width     = "0.7cm") %>% # set
      column_spec(3,width     = "0.7cm") %>% # fl 
      column_spec(4,width     = "0.7cm") %>% # wt   
      column_spec(5,width     = "0.7cm") %>% # sex 
      column_spec(6,width     = "0.7cm") %>% # mat
      column_spec(7,width     = "0.7cm") %>% # oto
      column_spec(8,width     = "0.7cm") %>% # dna
      column_spec(9,width     = "0.7cm") %>% # cnt        
      column_spec(10,width    = "1.1cm") %>% # prop m
      column_spec(11,width    = "0.7cm") %>% # male
      column_spec(12,width    = "0.7cm") %>% # female
      column_spec(13,width    = "0.7cm") %>% #  no sex  
      column_spec(14,width    = "1.0cm") %>% # re
      column_spec(15,width    = "1.2cm") %>% # bc
      column_spec(16,width    = "0.8cm") %>% # hybrid 
      row_spec(0, bold = T) %>%
      row_spec(20,  hline_after = T) %>%
      row_spec(row.count, bold = T)

```
\clearpage

<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
