<!-- The following code should appear at the beginning of the first appendix.
(if you have one)
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# LIST OF SABLEFISH RESEARCH AND ASSESSMENT SURVEYS. {#app:first-appendix}

```{r appendixA, results="asis"}

   dtBW   <- paste('exec dbo.procRKnitr_SurveyTrips ', yr ,sep='')
   trip   <- GetSQLData(dtBW,"Sablefish")
   write.table(trip, file = paste(path,'appendixA.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   trip   <-  read.csv(paste(path,'appendixA.csv',sep=''),header=T)
   
   colnames(trip) <- c("Year", "Dates",  "Vessel", "Captain", "Set Count", "GFBIO Id")
   kableExtra::kable(trip,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     format = "latex")  %>%
   kableExtra::kable_styling(font_size = 8) %>% 
                     row_spec(0, bold = T)

```

\clearpage

# DATA FORMS 2020 SABLEFISH SURVEY. {#app:second-appendix}

```{r appendixB,out.width = "480px", out.height = "406px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_BridgeLogIns3.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure C.1. Example of a completed bridge log data form with directions from the 2020 survey instruction manual.

\clearpage

```{r AppendixB2,out.width = "500px", out.height = "452px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_SetLogIns.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure C.2.  Example of a completed set log data form with directions from the 2020 survey instruction manual.

\clearpage

```{r AppendixB3,out.width = "500px", out.height = "476px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_CatchLogIns.png',sep='')
      knitr::include_graphics(img) 
      
```
Figure C.3.  Example of a completed catch log data form with directions from the 2020 survey instruction manual.
\clearpage

```{r AppendixB4,out.width = "500px", out.height = "426px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_CatchLogTabIns.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure C.4.  Example of a tabular catch log data entry form transposed from the catch log in Figure C.3. Directions from the 2020 survey instruction manual. 

\clearpage

```{r AppendixB5,out.width = "480px", out.height = "588px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_LSWMOIns.png',sep="")
      knitr::include_graphics(img) 
      
```
Figure C.5.  Example of a completed Sablefish biological sampling form and directions from the 2020 survey instruction manual. 

\clearpage

```{r AppendixB6,out.width = "500px", out.height = "501px", fig.align="left"}

      if(knitr:::is_latex_output())
      img <-  paste(basepath,'figures/AppendixB_TaggingSheetIns.png',sep="")
      knitr::include_graphics(img) 
      
```

Figure C.6.  Example of a completed tagging form with directions from the 2020 survey instruction manual.

\clearpage

# SET DETAILS `r yr`. {#app:third-appendix}
Details of sets completed during the `r yr` survey program (F/V `r boat`).  Sets are listed by stratum/inlet name, set type, depth stratum, start date, end of gear deployment time and duration in minutes. The depth strata for type 3 tagging sets include RD~1~ (100-250 fathoms), RD~2~ (250-450 fathoms) and RD~3~ (450-750 fathoms). The position data includes the major area and start and end latitude and longitude in degrees decimal minutes. The bottom depths (in meters) of the fishing set are shown with the mean bottom depth calculated from recordings at one minute intervals between the start and end of the set. The number of traps fished for each set excludes open traps, while holed or fouled traps have been included.  Sets that successfully deployed a Seabird SBE temperature and pressure recorder, a Hobo accelerometer or a Concerto CTD are indicated with an 'x'.


```{r appendixC, results="asis"}
   library(kableExtra)
   yr <- 2020
   options(knitr.kable.NA = '')  # get rid of NAs
   srvyset <-  paste('dbo.procRReport_Survey_SetDetails ',yr,',1,',setcnt, sep='')
   ssdat   <-  GetSQLData(srvyset,"Sablefish")
   write.table(ssdat, file = paste(path,'AppendixC.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   ssdat   <-  read.csv(paste(path,'AppendixC.csv',sep=''),header=T)
   
   latcnt  <-  length(ssdat[, 9])
               for (i in 1:latcnt)
                      { ssdat[i,9]= paste(ssdat[i,9],'째 ', ssdat[i,10],"'N",sep="")  }
   latcnt  <-  length(ssdat[,11])
               for (i in 1:latcnt)
                      { ssdat[i,11]=paste(ssdat[i,11],'째 ', ssdat[i,12],"'W",sep="") }
   latcnt  <-  length(ssdat[,13])
               for (i in 1:latcnt)
                      { ssdat[i,13]=paste(ssdat[i,13],'째 ', ssdat[i,14],"'N",sep="") }
   latcnt<-length(ssdat[,15])
               for (i in 1:latcnt)
                      { ssdat[i,15]=paste(ssdat[i,15],'째 ', ssdat[i,16],"'W",sep="") }
   
   ssdat  <-  ssdat[,c(-22,-23,-24)]  #no hobo, ctd or camera columns needed 2020
   ssdat  <-  ssdat[,c(-10,-12,-14,-16)]  
   
   colnames(ssdat) <- c( "Spatial Stratum", "Set",       "Type",      
                         "Depth Stratum",   "Date",      "Time", 
                         "Duration (minutes)",        "Area", 
                         "Start Latitude",        "Start Longitude", 
                         "End Latitude",        "End Longitude", 
                         "Start Depth (m)",           "End Depth (m)",       "Mean Depth (m)", 
                         "Traps Fished", 
                         "SBE 39")
 
   kableExtra::kable(ssdat,
                    booktabs  = TRUE, 
                    longtable = T,
                    linesep   = "",
                    format    = "latex") %>%
   kableExtra::kable_styling(font_size = 8, latex_options = "repeat_header",
               repeat_header_text = "continued.", repeat_header_method = "replace") %>%
   kableExtra::landscape() %>%
    
   row_spec(0, bold = T)  %>%     
   column_spec(1,width    = "1.1cm") %>%
   column_spec(2,width    = "0.5cm") %>%  # set
   column_spec(3,width    = "0.4cm") %>%  # type 
   column_spec(4,width    = "1.0cm") %>%  # depth stratum
   column_spec(5,width    = "0.9cm") %>%  # date
   column_spec(6,width    = "0.7cm") %>%  # time      
   column_spec(7,width    = "0.9cm") %>%  # dur
   column_spec(8,width    = "0.5cm") %>%  # area   
   column_spec(9,width    = "1.5cm") %>%  # lat
   column_spec(10,width   = "1.6cm") %>%
   column_spec(11,width   = "1.5cm") %>%
   column_spec(12,width   = "1.6cm") %>% 
   column_spec(13,width   = "0.7cm") %>%  # start
   column_spec(14,width   = "0.7cm") %>%      
   column_spec(15,width   = "0.5cm") %>%  # mean
   column_spec(16,width   = "0.6cm") %>%  # tf
   column_spec(17,width   = "0.4cm") %>% 
   column_spec(18,width   = "0.4cm") %>% 
   column_spec(19,width   = "0.4cm") %>%  # ctd 
   sub("\\caption\\[\\]\\{\\}", "\\caption*{}", .)
``` 

\clearpage


# SUMMARY OF BASKET USE BY TRAP `r yr`.{#app:fourth-appendix} 

Summary of the basket use by trap number for StRS sets during the `r yr` sablefish survey. The fate of the sablefish catch for each set and trap is indicated using the following abbreviations:
D = Discarded after weighing (processed as commercial catch), A = Sampled for LSMWO, T = Tagged and released, SD = Sublegal discarded, F= Frames, NULL = No sablefish catch/Trap missing. 

```{r appendixD, echo=FALSE}
   # Sablefish.dbo.procRReport_Survey_TrapUse procedure pulls data from table dbo.GFBIO_TRAPS_USE created by procedure 
   # Sablefish.dbo.Build_BIO_Sablefish_Tables
   options(knitr.kable.NA = '')
   trap       <- paste("dbo.procRReport_Survey_TrapUse ",yr,",1,",setcnt, sep="")
   trapdat    <- GetSQLData(trap,"Sablefish")
   write.table(trapdat, file = paste(path,'appendixD.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   trapdat    <- read.csv(paste(path,'appendixD.csv',sep=''),header=T)
   trapuse    <- trapdat[,c(-1)] 
   trapuse2   <- trapuse[,c(-27,-28)]

   
   kableExtra::kable(trapuse2,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     format = "latex")   %>%
      
   kableExtra::kable_styling(font_size = 6, 
                     latex_options = "repeat_header",
                     repeat_header_text = "continued.", 
                     repeat_header_method = "replace") %>%  
      
   kableExtra::landscape()  %>%
       #row_spec(38:52, color="blue"  )   %>%  no visits to inlets in 2020 = no blue font
       row_spec(0, bold=T) %>%
       column_spec(1,width      = "0.3cm") %>%
       column_spec(2,width      = "0.3cm") %>%
       column_spec(3,width      = "0.3cm") %>%
       column_spec(4,width      = "0.3cm") %>%
       column_spec(5,width      = "0.3cm") %>%
       column_spec(6,width      = "0.3cm") %>%
       column_spec(7,width      = "0.3cm") %>%
       column_spec(8,width      = "0.3cm") %>%   
       column_spec(9,width      = "0.3cm") %>%   
       column_spec(10,width     = "0.3cm") %>%
       column_spec(11,width     = "0.4cm") %>%
       column_spec(12,width     = "0.4cm") %>%
       column_spec(13,width     = "0.4cm") %>%
       column_spec(14,width     = "0.4cm") %>%
       column_spec(15,width     = "0.4cm") %>%
       column_spec(16,width     = "0.4cm") %>%
       column_spec(17,width     = "0.4cm") %>%
       column_spec(18,width     = "0.4cm") %>%
       column_spec(19,width     = "0.4cm") %>%
       column_spec(20,width     = "0.4cm") %>%
       column_spec(21,width     = "0.4cm") %>%  
       column_spec(22,width     = "0.4cm") %>% 
       column_spec(23,width     = "0.4cm") %>%       
       column_spec(24,width     = "0.4cm") %>% 
       column_spec(25,width     = "0.4cm") %>%
       column_spec(26,width     = "0.4cm") %>%      
       column_spec(27,width     = "0.4cm") %>%  
       column_spec(28,width     = "0.4cm") 
```

\clearpage

# SUMMARY OF SABLEFISH BIOLOGICAL DATA `r yr`. {#app:fifth-appendix} 
Biological data collected for sablefish by set, catch weight in kilograms and numbers of fish.  Details include a tally of specimens recovered, tagged and sampled.  Mean fork lengths for tagged sablefish and sampled male and female sablefish are listed.  


```{r appendixE, echo=FALSE}
   #  sql query for inline text
   #  Sablefish.dbo.procReport_Survey_SampleDetails pulls data from table GFBIO_RESEARCH_SAMPLE_DETAILS built by     
   #  procedure Sablefish.dbo.Build_BIO_Sablefish_Tables 
   samples               <-  paste("dbo.procReport_Survey_SampleDetails ",yr,",1,",setcnt, sep="")
   surveyspec            <-  GetSQLData(samples,"Sablefish")
   write.table(surveyspec, file = paste(path,'appendixE.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   surveyspec            <-  read.csv(paste(path,'appendixE.csv',sep=''),header=T)
   count.row.total       <-  length(surveyspec$SET)
   count.row             <-  length(surveyspec$SET) - 1
   surveyspec$SET[count.row.total]<- "Total"

   
   colnames(surveyspec)  <-  c("", "kg", "Count", "Recover-Rerelease", "Deceased", "Released", 
                              "Count",  "Mean", "Fork Length", "Sex", "Maturity", "Otoliths",
                              "Weight", "Count", "Proportion Males", "Males", "Females")

   kableExtra::kable(surveyspec,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     align=rep('r', 17),
                     format = "latex") %>%
      
   add_header_above(c("Set"= 1,
                      "Total Catch" = 2, 
                      "Tagged Fish Counts" = 3,  
                      "Tagged Fork Lengths(mm)" = 2,
                      "Specimen Count"= 6, 
                      "Mean Fork Length(mm)" = 3), bold = TRUE) %>%
   kableExtra::kable_styling(font_size = 8, latex_options = "repeat_header",
                    repeat_header_text = "continued.", repeat_header_method = "replace") %>%     
   
   kableExtra::landscape()  %>%
   row_spec(0, bold = T)  %>%   
   column_spec(1,width    = "0.4cm") %>%  # set
   column_spec(2,width    = "0.7cm") %>%  # kg
   column_spec(3,width    = "0.9cm") %>%  # count
   column_spec(4,width    = "0.9cm") %>%  # rr
   column_spec(5,width    = "1.0cm") %>%  # decease
   column_spec(6,width    = "0.9cm") %>%  # rel     
   column_spec(7,width    = "1.5cm") %>%  # count
   column_spec(8,width    = "0.9cm") %>%  # mean
   column_spec(9,width    = "0.7cm") %>%  # fl
   column_spec(10,width   = "0.6cm") %>%  # sex
   column_spec(11,width   = "0.7cm") %>%  # mat
   column_spec(12,width   = "0.7cm") %>%  # oto 
   column_spec(13,width   = "0.6cm") %>%  # wt
   column_spec(14,width   = "0.6cm") %>%  # cnt
   column_spec(15,width   = "1.1cm") %>%  # prop m
   column_spec(16,width   = "0.7cm") %>%  # male         
   column_spec(17,width   = "0.7cm") %>%  # fem
   row_spec(count.row.total, bold = T)  %>%    
   row_spec(count.row,  hline_after = T)

```
\clearpage

# SUMMARY OF BIOLOGICAL DATA FOR ROUGHEYE/BLACKSPOTTED ROCKFISH COMPLEX. {#app:seventh-appendix} 
Biological data collected for rougheye/blackspotted rockfish complex.  Each set is listed with counts of specimens sampled, calculations of mean fork lengths and number of species visually identified as either a RE = rougheye rockfish, BS = blackspotted rockfish or a hybrid.

```{r appendixF, echo=FALSE}
   yr=2020
   othersamples <-  paste( "select species_name, [SET], [Len Sample Count], [weight_count], [Sex Sample Count], ",
                           "[Maturity Sample Count], [Otolith Sample Count], [DNA Sample Count], ",
                           "Sample_count, [Proportion Males],  ",
                           "round([Male Mean Fork Len(mm)],0) as malelen, ",
                           "round([Female Mean Fork Len(mm)],0) as femlen,  ", 
                           "round([NoSexMeanLen(mm)],0) as nosexlen, bsre.Rougheye, bsre.Blackspotted, bsre.Hybrid ",
                           "from  (select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "SUM(re) AS Rougheye, SUM(bs) AS Blackspotted, SUM(hyb) AS Hybrid ",
                           "from  (select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 16 THEN 1 ELSE 0 END AS re, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 17 THEN 1 ELSE 0 END AS bs, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 31 THEN 1 ELSE 0 END AS hyb, ",
                           "SPECIMEN_ID ",
                           "from dbo.gfbio_species_guess) AS bs ",
                           "group by year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE) AS bsre RIGHT OUTER JOIN ",
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ON bsre.TRIP_ID = ",              
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.TRIP_ID ",
                           "and bsre.FE_MAJOR_LEVEL_ID = dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.[SET] ",
                           "AND bsre.SPECIES_CODE = ",                       
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.species ",            
                           "where (dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.Year = ",yr, 
                           ") order by species,[SET]", sep="")
   otherspec2            <-  GetSQLData(othersamples,"Sablefish")   # read from SQL Server
   write.table(otherspec2, file = paste(path,'appendixF.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   otherspec2            <-  read.csv(paste(path,'appendixF.csv',sep=''),header=T) # read from csv
   otherspec2$species_name<-as.character(otherspec2$species_name)
   addition              <-  c('Total','', sum(otherspec2$Len.Sample.Count),sum(otherspec2$weight_count), sum(otherspec2$Sex.Sample.Count),
                               sum(otherspec2$Maturity.Sample.Count), sum(otherspec2$Otolith.Sample.Count),sum(otherspec2$DNA.Sample.Count),
                               sum(otherspec2$Sample_count),'','','','','','','')
   otherspec             <-   rbind(otherspec2,addition)
   row.count             <-   length(otherspec$species_name)
  
   otherspec$species_name<-  cleanf(otherspec$species_name) 
   colnames(otherspec)   <-  c("Species Name", "Set", "Fork Length","Weight", "Sex", "Maturity", "Otolith", 
                               "DNA",  "Total Count", "Proportion Males",  "Males", "Females",  
                               "No sex", "RE", "BS","Hybrid" )
   
      kableExtra::kable(otherspec,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     align=c('l', 'r','c','c','c','c','c','c','c','c','c','c','c','c','c','c'),
                     format = "latex") %>%
      
      add_header_above(c(" "= 2,
                      "Specimen Count"= 7, 
                      "Mean Fork Length(mm)" = 4,
                      "Sampler Visual id Count" = 3), bold=TRUE) %>%
   
      kableExtra::kable_styling(font_size = 8, 
                      latex_options = "repeat_header",
                      repeat_header_text = "continued.", 
                      repeat_header_method = "replace") %>%
      
      kableExtra::landscape()  %>% 
         
      column_spec(1,width     = "3.5cm") %>% # species
      column_spec(2,width     = "0.7cm") %>% # set
      column_spec(3,width     = "0.7cm") %>% # fl 
      column_spec(4,width     = "0.7cm") %>% # wt   
      column_spec(5,width     = "0.7cm") %>% # sex 
      column_spec(6,width     = "0.7cm") %>% # mat
      column_spec(7,width     = "0.7cm") %>% # oto
      column_spec(8,width     = "0.7cm") %>% # dna
      column_spec(9,width     = "0.7cm") %>% # cnt        
      column_spec(10,width    = "1.1cm") %>% # prop m
      column_spec(11,width    = "0.7cm") %>% # male
      column_spec(12,width    = "0.7cm") %>% # female
      column_spec(13,width    = "0.7cm") %>% #  no sex  
      column_spec(14,width    = "1.0cm") %>% # re
      column_spec(15,width    = "1.2cm") %>% # bc
      column_spec(16,width    = "0.8cm") %>% #  hybrid 
      row_spec(0, bold = T) %>%
      row_spec(20,  hline_after = T) %>%
      row_spec(row.count, bold = T)

```
\clearpage

<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
